### 2022-04-20 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@db274119a671a5a4aedb594967efcbc6a1d2cc1c 🚀

In this paper, we examine the biogeographic structure of
bats-betacoronaviruses associations, based on a curated dataset of known
and recently discovered hosts. This work is important both as a
description of the bats-betacoronavirus complex, but aslo because more
broadly, bats are known reservoirs for a variety of emerging viruses and
pathogens (Calisher et al. 2006, Melaun et al. 2014), making balancing
the needs for bat conservation and disease prevention a potentially
difficult act and a source of human-wildlife conflicts, especially in
more densely populated areas (Stone et al. 2015, Rego et al. 2015). By
drawing on concepts from the Geographic Mosaic Theory of Coevolution
(Thompson 2005), we turn these associations into a spatially explicit
additive mapping of zoonotic risk components, which reveals extreme
heterogeneity of risk at the global scale; furthermore, we identify the
Amazon and South-Eastern Asia as hotspots of phylogenetic
distinctiveness of betacoronaviruses; surprisingly, current data suggest
that viral sharing between hosts in high in the Amazon and low in
South-Eastern Asia, which has the potential to result in different
evolutionary dynamics between these two regions.

>>>>

In this paper, we examine the biogeographic structure of
bats-betacoronaviruses associations, based on a curated dataset of known
and recently discovered hosts. This work is important both as a
description of the bats-betacoronavirus complex, but aslo because more
broadly, bats are known reservoirs for a variety of emerging viruses and
pathogens (Calisher et al. 2006, Melaun et al. 2014), making balancing
the needs for bat conservation and disease prevention a potentially
difficult act and a source of human-wildlife conflicts, especially in
more densely populated areas (Stone et al. 2015, Rego et al. 2015). By
drawing on concepts from the Geographic Mosaic Theory of Coevolution
(Thompson 2005), we turn these associations into a spatially explicit
additive mapping of zoonotic risk components, which reveals extreme
heterogeneity of risk at the global scale; furthermore, we identify the
Amazon and South-Eastern Asia as hotspots of phylogenetic
distinctiveness of betacoronaviruses (Anthony et al. 2017);
surprisingly, current data suggest that viral sharing between hosts in
high in the Amazon and low in South-Eastern Asia, which has the
potential to result in different evolutionary dynamics between these two
regions.
